\chapter{Exercise 3: Matching Any Character}

Finding words is nice, but you can just do that with normal
string operations.  What about finding \emph{patterns} of text?
The first kind of pattern is to have a regex match any single 
character.  You do this with the '.' (dot) operator, which
says "match any one character here".

Continuing with the corpus we've been using, here's
a new script for you to type:

\begin{code}{ex3.regex}
\begin{Verbatim}
<< d['code/ex3.regex|dexy'] >>
\end{Verbatim}
\end{code}

You can see I'm sort of searching for the same things as before, but instead
of the actual words, I'm putting a random '.' (dot) character to make that
character a variable match.

\section{What You Should See}

When you run this against \file{ex2.txt} you should see this:

\begin{code}{ex3.out}
\begin{Verbatim}
<< d['code/ex3.out|dexy'] >>
\end{Verbatim}
\end{code}

That should be close to what you expected, except for the matches for
\verb|y....| which matches \emph{both} lines.  The reason is it matches
"yard." from the 2nd line as you expect, but it also matches "y dog"
from the first line.  See how it's a 'y' and 4 characters?  The regex
doesn't care that those characters are chunks of two words, it will match
them without any knowledge of the English language.


\section{Extra Credit}

\begin{enumerate}
\item Use !match to switch from search to match mode and then see if you
    get the same results.  Why?
\item Write a line of only '.' (dot) sequences that matches the 2nd line
    but not the first.
\item Using a '\verb|\|' (backslash) let's you escape the '.' to tell the regex
    that you mean "no actually match this as a ."  Use that to fix the
    3rd regex so it only matches the 2nd line of the corpus.
\item Change the corpus such that you write two new lines but they still
    match the same as the other corpus.
\end{enumerate}

\section{Portability Notes}

Some regular expression engines mean different things when they say "everything".
In Python "everything" means, "Well, not newline chars or just random stuff
we decided wasn't really everything."  Others actually really mean everything.
It all depends on the engine and what they did with it.

